\mytitle

### 2021-12-22 paper.tex
adding citation

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[german]{authblk}
\usepackage[format=plain,labelfont={bf}]{caption}
\usepackage{listings}
\usepackage[shortcuts]{extdash} % \-/
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage[sorting=none,citestyle=numeric-comp]{biblatex}
\addbibresource{paper.bib}

@@

As is well known, the performance of this naive implementation can be
improved by applying Horner's scheme, which reduces the number of
expensive floating\-/point multiplications to 7 and requires 6
additions:
%
\begin{align}
\begin{split}
  \ln(1+x) \approx{}& x \bigg\{1 + x \bigg[-\frac{1}{2} + x \bigg(\frac{1}{3} + x \bigg\{-\frac{1}{4} \\
  &+ x \bigg[\frac{1}{5} + x\bigg(-\frac{1}{6} + \frac{x}{7}\bigg)\bigg]\bigg\}\bigg)\bigg]\bigg\}.
\end{split}\label{eq:horner}%
\end{align}
%
A C implementation using Horner's scheme could read
%
\lstinputlisting[language=C]{src/log1p_horner.c}
%
Note, that the formulation using Horner's scheme requires the
evaluation of the floating\-/point operations in strictly sequential
order.  However, the significant reduction of the number of
floating\-/point multiplications, compared to the naive
implementation, usually results in a shorter run\-/time.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[german]{authblk}
\usepackage[format=plain,labelfont={bf}]{caption}
\usepackage{listings}
\usepackage[shortcuts]{extdash} % \-/
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage[sorting=none,citestyle=numeric-comp,eprint=false,isbn=false]{biblatex}
\addbibresource{paper.bib}

@@

As is well known, the performance of this naive implementation can be
improved by applying Horner's scheme \cite{horner}, which reduces the
number of expensive floating\-/point multiplications to 7 and requires
6 additions:
%
\begin{align}
\begin{split}
  \ln(1+x) \approx{}& x \bigg\{1 + x \bigg[-\frac{1}{2} + x \bigg(\frac{1}{3} + x \bigg\{-\frac{1}{4} \\
  &+ x \bigg[\frac{1}{5} + x\bigg(-\frac{1}{6} + \frac{x}{7}\bigg)\bigg]\bigg\}\bigg)\bigg]\bigg\}.
\end{split}\label{eq:horner}%
\end{align}
%
A C implementation using Horner's scheme could read
%
\lstinputlisting[language=C]{src/log1p_horner.c}
%
Note, that the formulation using Horner's scheme requires the
evaluation of the floating\-/point operations in strictly sequential
order.  However, the significant reduction of the number of
floating\-/point multiplications, compared to the naive
implementation, usually results in a shorter run\-/time.
